Sensitivity Analysis

### 2023-09-27 SFE_article_Sensitivity_Analysis/Article_Model_Parameters.tex
27.09

>>>>

The sensitivity analysis is a tool to understand the parametric dependence of dynamic behavior and its suitability in inferring mechanisms of the dynamic behavior of the analyzed system. The mathematical formulation involves derivative-based local sensitivity analysis of the solution of an inverse problem with respect to perturbations of parameters. The local method is based only on considering all parameters as constants (those independent of time or location), and then the sensitivity coefficients are estimated by solving a variational system simultaneously with the original system. The sensitivity equations can be obtained in various ways, but in the case of this work, the automatic differentiation technique was implemented to obtain the sensitivity equations. By identifying which parameters are influential at specific time points during the simulation, local sensitivity analysis can yield valuable information for guiding the design of experiments, the process modeling, or the model reduction. The local sensitivity analysis techniques consider the sensitivities at only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear system.

In this study, the local sensitivity analysis method was introduced to explore the dynamics of the supercritical extraction system, which consists of a set of partial differential equations. The sensitivity equations evaluate the influence of control variables such as flow rate, pressure, and inlet temperature on the state-space consisting of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield. Every change in the control variables leads to a state-space change, eventually affecting the process performance. This information can be utilized to identify which control variables influence the extraction yield the most. The control with high sensitivities on the extraction should be further investigated to find optimal operating conditions.

### 2023-09-27 SFE_article_Sensitivity_Analysis/Sections/Results_Sensitivity.tex
27.09

    A change in flow rate has a direct impact on the kinetic energy of the fluid, as defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$. The consequence of Equation \ref{EQ:Velocity} is the instantaneous change of the velocity field in the system, which means that the spatial derivative equals zero. Because ${\color{blue}h}$ represents an enthalpy but not a total enthalpy, it does not contain the kinetic energy contribution. Consequently, under conditions where the thermodynamic state remains constant, specifically with constant temperature and pressure, Figure \ref{fig:Sensitivty_F_H} demonstrates no significant deviation.

>>>>

    A change in flow rate is defined by the spatial derivative $\frac{\partial \left( {\color{orange}\rho_f}{\color{blue}h} A_f v \right)}{\partial {\color{blue}z}}$. The consequence of Equation \ref{EQ:Velocity} is the instantaneous change of the velocity field in the system, which means that the spatial derivative equals zero. Because ${\color{blue}h}$ represents an enthalpy but not a total enthalpy, it does not contain the kinetic energy contribution. Consequences of the modelling assumptions are that ${\color{blue}h}$ and ${\color{orange}\rho_f}$ change only if a pressure or temperature change directly. As the result, Figure \ref{fig:Sensitivty_F_H} demonstrates no significant deviation.
